Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-20 response-to-reviewers.tex

  \begin{response}
    No response needed here.
  \end{response}
\item 
  My main concern is with some of their wage results. I find it
  puzzling that they don’t find a wage premium for Russian men who
  have Estonian language skills as they do find a sizeable significant
  effect of about 11 to 17 percent for Russian women and a significant
  positive effect for Estonians who speak Russian. Furthermore, they
  find that Estonian language skills do reduce the probability of
  being unemployed for Russians. Why is there a reduction in the
  probability of being unemployed, but no wage effect? Can we trust
  this result? Looking at the descriptive statistics (see Table 1) the
  wage for Russian men who speak Estonian seems to be higher compared
  to Russian men without the ability to speak Estonian (489.96 vs
  401.59). The authors should either provide more statistics on this
  result (if possible) or a more detailed discussion on potential
  reasons that lead to this finding.

  \begin{response}
    This is a good point.  We have added some more analysis (see
    Section 7), and it appears the story is somewhat more nuanced.
  \end{response}
\item
  \debug{OT: I'll do a rewrite after changes are made, hope it's
    sufficient.} 
  The paper needs to be checked for spelling and grammar
  errors. There are a number of typos and errors, which should be
  corrected in a revision. This would normally be a minor comment, but
  here the authors should take this comment very serious as there are
  so many mistakes.
\end{enumerate}

\subsection{Minor comments:}

\begin{enumerate}
\item- The description of the estimation models in Chapter 4 should
  be more detailed. Please describe more specifically what exactly you
  are estimating. In particular the description of the second model
  estimating the time trend is very short.

  \begin{response}
    We have improved and simplified the description of the model and related variables.
  \end{response}
  \fxwarning{ot: should you cluster if you do random effects?}
\item - The tables and figures should have notes that explain in more
  detail what is shown in the respective table and figure. For
  instance, the table notes should contain the included control
  variables, the sample period and the age restriction applied.
  \debug{SKB: I added this information to the tables and the figures. The descriptions might need some polishing still.}
\item 
- Page 4: You write that you are only analysing individuals who are
working or actively looking for a job, but in line 35 on the same page
you write that inactivity is one of the included labour market
outcomes. Please clarify this and be clear in your description of what
is included in your sample.
\item 
  \debug{ot: let's make it equal (i.e. remove all observations with
    any of the variables missing.  Add a footnote that when we
    included all the variables, we still got the same results.}
\debug{SKB: I estimated the models and updated the tables with occupation added to Model 3. Added footnote linking to original tables with \enquote{unrestricted} observations}
  The sample size for different specification of the same analysis
should be the equal. Otherwise it is difficult to conclude whether the
changes in the coefficients are coming from the addition of more
controls or form the change in the size of the estimation sample.
\item 
- In the paper, you are only showing the results of the variables of
interest. I suggest to provide tables including all coefficients (not
the year dummies) in the Appendix. It might be interesting to see how
the coefficients of the control variables change across the different
models.
\debug{SKB: Will add them after I figured out how to present the results nicely formatted. It boils down to finding the right options for the \enquote{estout} or the \enquote{outtex/outreg} user provided package in Stata. I could do the formatting in Excel myself, but I prefer the Stata solution. }
\debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct. The tables are not linked yet to the main text.}
\debug{SKB: Should I include tables for unemployment as well? This would blow up the number of pages even further. I could drop the standard errors to save space. Let me know what would be best.}
\item 
- All tables: Be consistent in the description of your tables. The
table notes and the labels for e.g., "observations", are inconsistent
across the different tables. 
\debug{SKB: Fixed. Changed obs to Observations in tables}
\item
  \debug{ot: this was because of both 'B. Chiswick' and
    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
    distinguish between these two guys.}
 Page 1: To cite Chiswick you are using different versions
(B. Chiswick and B. R. Chiswick).

### 2018-07-20 paper/ijm.tex
model description improved

We describe the outcome of individual $i$ belonging to group $g$ (either Estonian
or Russian) at year $t$ as
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} ^{g} = &\: \alpha^{g}{}' \vec{X}_{it}^{g} + \vec{\beta}^{g}{}' \vec{L}_{it}^{g} +
		\eta_{i}^{g} +
		\upsilon_{t} + \epsilon_{it}^{g},
	\end{split}
\end{equation}
where $y$ is the outcome (either unemployment indicator
or logarithm of net monthly wage), $\vec{X}$ are the other individual
characteristics; $\vec{L}$ is the vector of
language skill descriptors, $\eta_{i}^{g}$ is the individual-specific effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}^{g}$
is the idiosyncratic error term. 
\fxerror{ot: what's the eta term?  do you do random effects?}
\fxerror{SKB: Eta should be the individual specific random effect. We cluster the standard errors at the individual level, hence estimate a random-effect model, although not a panel random-effect model.}
\fxerror{ot: why does $\upsilon$ have index $g$?}
\fxerror{SKB: Should be an error, probably index $g$ was just added to everything.}
As we use panel data, we cluster the
standard errors on individuals.  When analysing the long-term time
trend, we use the same specification (without year fixed effects) to
estimate separate models for each individual year.

We estimate three models that differ in terms of the number of
control variables. The first specification only includes the language skills
and year dummies.  It describes the ``raw'' effect of language skills
on outcomes after controlling for substantial time trends in our data.
The second specification additionally includes individual
characteristics (age, education) and family descriptors (marital
status, indicator for inter-ethnic marriage, having kids up to 17 years
old) and county of residence.  
Finally, the third specification also adds industry, occupation, and other
workplace descriptors.
Note that in case of unemployment probability,
we only estimate the first two models.
\fxnote{Actually, I tried to estimate Model 3 as well for unemployment probability. The language coefficients become insignificant after controlling for industry and occupation. Hence, Estonian language fluency lowers the unemployment probability only if workplace characteristics are ignored. Since nobody questioned this result during review, we should maybe not mention it now. }

>>>>

We describe the outcome of individual $i$ at year $t$ as
\begin{equation}
	\label{eq:specification}
	\begin{split}
		y_{it} = &\: \vec{\alpha}{}' \vec{X}_{it} + \vec{\beta}{}' \vec{L}_{it} +
		\eta_{i} +
		\upsilon_{t} + \epsilon_{it},
	\end{split}
\end{equation}
where $y$ is the outcome (either unemployment indicator
or logarithm of net monthly wage), $\vec{X}$ are the individual and
workplace descriptors; $\vec{L}$ is the vector of
language skill descriptors, $\eta_{i}$ is the individual random effect, $\upsilon_{t}$ are the year dummies and $\epsilon_{it}$
is the idiosyncratic error term.  We estimate separate models for
Estonians and Russians.
\fxnote{ot: if you do random effects--do you still have to cluster?}
As we use panel data, we cluster the
standard errors on individuals.  When analysing the long-term time
trend, we use the same specification (without year fixed effects) to
estimate separate models for each individual year.

We estimate three models that differ in
control variables. The first specification only includes the language skills
and year dummies.  It describes the ``raw'' effect of language skills
on outcomes after controlling for substantial time trends in our data.
The second specification additionally includes individual
characteristics (age, education) and family descriptors (marital
status, indicator for inter-ethnic marriage, having kids up to 17 years
old), and county of residence.  
Finally, the third specification also adds industry, occupation, and other
workplace descriptors.
Note that in case of unemployment probability,
we only estimate the first two models.
\fxnote{Actually, I tried to estimate Model 3 as well for unemployment probability. The language coefficients become insignificant after controlling for industry and occupation. Hence, Estonian language fluency lowers the unemployment probability only if workplace characteristics are ignored. Since nobody questioned this result during review, we should maybe not mention it now. }
